---
title: "Gaming Info"
author: "Kenny Nguyen, Peter Miyoshi, Ryan McGhee"
date: "2/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Domain/Data

We are interested in gaming as a domain because it explores a realm of technology that has gained traction and popularity over time, producing complex and interesting advancements in elements such as gaming platforms, companies, and technological innovations (VR, mobile, etc.) Our group has played different video games throughout our lives and it would be interesting to see how our perspective of its evolution parallels trends we uncover. Our merged dataset, sourced  [here](https://www.kaggle.com/jummyegg/rawg-game-dataset/data) from Trung Hoang and [here](https://www.kaggle.com/ashaheedq/video-games-sales-2019) from Abdulshaheed Alqunber contains information about many games both old and recent! Both authors published their data through Kaggle.


## Summary Paragraph
```{r summary_info, include=FALSE, echo=FALSE}
source("scripts/summary_information.R")
summary_data <- read.csv("data/merged_game_data.csv", stringsAsFactors = FALSE)
list <- get_summary_info(summary_data)
```

Merging together Hoang and Alqunber's data, we have information from **`r list$game_titles`** game titles. The earliest release date of a game in this dataset goes all the way back to **`r list$oldest_date`**. In addition, of those game titles there are **`r list$genres`** unique genre or genre combinations and **`r list$platforms`** platforms that these games have been played on! And of those platforms, the following are the top 3 with the most games made for it: **`r list$top_three_platforms`**. In total, the games from this set also brought in **`r list$sales`** sales globally!

## Summary Table
Here is a summary of our merged data, grouped by genre and sorted by the total games shipped decending.
```{r echo=FALSE}
source("scripts/summary_table.R")
agregate(summary_data)
```

The data was grouped in this way in order to help reveal what genres have been most successful over the years, and includes several different columns which could be used as measures of success, as well as a couple of columns we felt may contain interesting differences between the genres. Looking at the chart you can see that Role-Playing and Platform games are quite popular going by how many were shipped; Both being nearly twice the next highest genre. It is also clear from the chart that Average Playtime is unlikely to be an interesting column to investigate further, at least by genre. The averages are too low to show any major differences. Similarly, ratings between genres don't show huge differences between them, although between the lowest and highest there might be enough of a difference to be interesting. Finally, achievements might be an interesting category to look into further, as there is a wide range of different values between the genres. These could be due to outliers skewing the results, or perhaps there is actually a connection between genre and number of achievements.

## Chart 1: Kenny
This chart was intended to show the relationship between **playtime** (the hours needed to complete a game) and **critic score** to find out whether one's engagement with a game is significant to how those games are rated. For critic score, our merged dataset gives us the choice between using the _critic_score_ values from Alqunber or the _metacritic_ ratings from Hoang. We opted to use _metacritic_ because it shows aggregate review scores on a more nuanced scale (*0-100* compared to *1-10*).

```{r first_chart, message=FALSE, warning=FALSE, echo=FALSE}
source("scripts/first_chart.R")
get_first_chart(summary_data)
```

A scatter plot was used because:

- Playtime and metacritic score are continuous values which can have large amounts of variability.
- A non-linear regression could be plotted on top of points to show the general relationship between playtime vs. critic score.

The axes were also adjusted to remove outliers such as individual games with long playtime or trend lines with wide confidence intervals. In this chart, we can see that **higher metacritic ratings are correlated with longer playtime**. This may inform developers that adding elements to a game which increases playtime through replayability or bonus content may be worthwhile during game development.


## Chart 2: Peter
Describe the purpose of each chart (e.g., "this chart was intended to show the relationship between..."), render each chart, and describe pertinent observations found in each chart

```{r echo = FALSE}
source("scripts/second_chart.R")
get_second_chart(summary_data)
```


## Chart 3: Ryan
Describe the purpose of each chart (e.g., "this chart was intended to show the relationship between..."), render each chart, and describe pertinent observations found in each chart